---
title: "Predicting Overall Gross - Movie Data"
author: "Devin"
date: "5/31/2021"
output: html_document
---

```{r}
library(tidyverse)

data <- read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-10-23/movie_profit.csv') %>% 
  select(-X1)

data
```

Does the age old saying "You gotta spend money to make money" hold when accounting for total gross of movies?

Regression model shows production budget is a significant predictor of worldwide gross accounting for 43% of the variance in worldwide gross data but model diagnostics indicate non-normality of residuals and potential heterogeneity.
```{r}
budget_world <- lm(worldwide_gross ~ production_budget, data = data)

summary(budget_world)

broom::tidy(budget_world, conf.int = TRUE)

performance::check_model(budget_world)
```

To address this we run two robust versions of the model, first a robust model with heterogeneity consistent standard error estimates (using the HC4 method) and second, a bootstrapped model with 10,000 iterations (Usually bootstrapping is used for low sample size and while this is a large data set it is small when making inferences about films in general). 

Both models support the original coefficient estimate 2.65 and still show statistical significance with confidence intervals not including 0. 

Thus for every increase in production budget by 1 we should see an increase in worldwide gross by 2.65. 
```{r}
parameters::parameters(budget_world, robust = T, vcov.type = "HC4")
parameters::parameters(budget_world, bootstrap = T, iterations = 10000)
```


We do however have A LOT of other variables in this data set and could see if other features also predict worldwide gross. However instead of using step-wise regression we'll try out a LASSO model given the vast amount of coefficients we'd get by entering all features in the model (release year alone gives us well over 40 coefficients)

First we create an x and y for our lasso model. For x we remove worldwide gross (our y) along with movie name(a non meaningful feature) 
```{r}
x <- data %>% 
  drop_na() %>%
  select(-c(worldwide_gross, movie)) %>%
  data.matrix()

y <- data %>%
  drop_na() %>%
  select(worldwide_gross) %>%
  data.matrix()
```

We then build an intial lasso model using the glmnet function from the glmnet package and take a look at our coeffients
```{r}
lasso_model <- glmnet::glmnet(x,y)

lasso_model %>%
  broom::tidy()
```

In order to get a handle on all these estimates we'll build a cross validated version of the model using cv.glmnet and plot the model to see how how our much our mean squared error is reduced by each lambda
```{r}
cv_fit <- glmnet::cv.glmnet(x,y)
plot(cv_fit)
```

Using conservative lambda production budget and domestic gross appear to be the useful predictors in our model when predicting worldwide gross.
```{r}
cv_fit$glmnet.fit %>%
  broom::tidy() %>%
  filter(lambda == cv_fit$lambda.1se,
         term != "(Intercept)") %>%
  arrange(desc(estimate))
```

Finally, let's return to our classical regression and add in domestic gross in our model. WOW! We've got a model that accounts for 88% of the variance with domestic gross an even stronger predictor of worldwide gross. Robust models also support this conclusion.
```{r}
budget_wolrd_improved <- lm(worldwide_gross ~ production_budget + domestic_gross, data = data)

budget_wolrd_improved %>%
  summary()

budget_wolrd_improved %>%
  broom::tidy(conf.int = TRUE)
```

```{r}
performance::check_model(budget_wolrd_improved)
```

```{r}
parameters::parameters(budget_wolrd_improved, robust = T, vcov.type = "HC4")
parameters::parameters(budget_wolrd_improved, bootstrap = T, iterations = 10000)
```


Spend money to make money? In hollywood the answer is definitely yes but our analysis also shows that the money made domestically is a good predictor of how well a movie will do globally - at least with this data and for the time being.
